Beveridge Sequences

### 2022-11-09 Combinatorics/CatalanNumbers/document.tex
fixed typo

	\section{Introduction to the sequence}
	Our Catalan group is defined as a sequence of $a_1, \ldots, a_n+1$ of non-negative integers such that $\sumfrom{i=1}{n+1}{2^{-a_i}} = 1$ and for all $2 \leq j \leq n+1$ the number
	$2^{a_j} \sumfrom{i=1}{j-1}{2^{-a_i}}$ is an integer.  We will call any sequence that fits these rules a beveridge sequence.

>>>>

	\section{Introduction to the sequence}
	Our Catalan group is defined as a sequence of $a_1, \ldots, a_{n+1}$ of non-negative integers such that $\sumfrom{i=1}{n+1}{2^{-a_i}} = 1$ and for all $2 \leq j \leq n+1$ the number
	$2^{a_j} \sumfrom{i=1}{j-1}{2^{-a_i}}$ is an integer.  We will call any sequence that fits these rules a beveridge sequence.
